Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-29 Opsætningexam/DraftExam.tex
Få rettelser
e

\subsection{Model Limitations and Irrelevancy}
The necessity to exclude municipality dummies as regressors in the prediction models. Leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance. This makes distinction between municipality a lot more difficult as well as uncertain.   
Without the municipality dummies, the interpretation of the prediction results are more insecure. %Instead of predicting the valuation of a given estate, of a given type, in a given municipality or city. It predicts the valuation of a estate at a \textit{more or less} location in Denmark by type, only geographically controlled by distances to various conveniences. 
Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
If one intended to predict valuations country-wide more realistic, a model for each municipality could have been more satisfactory. Resulting in 98 separate models. The evident downside of this approach being the prospect of limitations in available data (some municipalities has very few listings).     
Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.

\section{Conclusion}
Even after regularization, and deliberate exclusion of features. Our model still suffers from overfitting. 

>>>>

\subsection{Model Limitations}
The necessity to exclude municipality dummies as regressors in the prediction models. Leaves the model to only separate municipalities by the socio-economic factors, which are subject to low variance. This makes distinction between municipality a lot more difficult as well as uncertain.   
Without the municipality dummies, the interpretation of the prediction results are more insecure. %Instead of predicting the valuation of a given estate, of a given type, in a given municipality or city. It predicts the valuation of a estate at a \textit{more or less} location in Denmark by type, only geographically controlled by distances to various conveniences. 
Geographical boundaries could have been limited way more, resulting in easier interpretation of predictions. Potentially by predicting only for a specific city or municipality. \\
If one intended to predict valuations country-wide more realistic, a model for each municipality could have been more satisfactory. Resulting in 98 separate models. The evident downside of this approach being the prospect of limitations in available data (some municipalities has very few listings).     
Another approach could have been to group cities which share characteristics. Ex. The three biggest cities, the provinces, the islands, the country-side towns.

\section{Conclusion}
In this assignment, we have used machine learning to train a model to predict valuation prices of real estate in Denmark. We did this by scraping Boliga.dk for all of their active houses for sale and combining this with municipal data on income, education, schools and urbanization. Additionally, we also scraped data from hvorlangterder.dk which calculates the distance from an address, to different every-day commodities such as hospitals, schools and shopping. 
We have explained how we carried out our gathering of data, how we have structured the data and how we cleaned it.

We performed descriptive statistics on the data to gain a better acquaintance with the data. 
We conducted feature selection by assessing the correlation between the different features and the target variable, which in our assignment has been the valuation price. 
We trained both a Lasso- and a Ridge regression model and compared their performances with the performance of a standard linear regression. Though k-fold cross-validation, we estimated the optimized hyperparameters for both regularization models. We found that the Ridge regression performed best on average, with the performance measure being the smallest mean square error of the model. 
We have assessed to which degree we have managed to find a good bias-variance-balance for our model and concluded that our model suffers from a degree of overfitting. This was done by examining the validation curve of our final model.

Finally, we have discussed the results of our analysis. We have critically assessed the boundaries of our research and drawn up potential possibilities for improvement.
